### 2014-02-22 paper/retrofit.tex
fix evalctx rule

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (iniTE (lconf id il tS ie))
.->
iconf iS' (iniTE (lconf id il' tS ie'))
|}

>>>>

\begin{mathpar}
\inferrule[I-evalCtx]
{|
iconf iS (tconf id il ie)
.->
iconf iS' (tconf id il' ie')
|}
{|
iconf iS (iniTE (lconf id il tS (iniE ie)))
.->
iconf iS' (iniTE (lconf id il' tS (iniE ie')))
|}
